Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-12-20 manuscript/main.tex
Add summary of coefficients learned across natural test data
Includes an updated analysis notebook, a new supplemental figure, and a brief
summary in the main results text.

To enable real-time forecasts, we integrated our forecasting framework into our existing open source pathogen surveillance application, Nextstrain \cite{Hadfield2018}, and used our best model to forecast A/H3N2 populations in September 2020.
Our combined HI cross-immunity, mutational load, and LBI model favored the growth of the currently circulating clade A1b/197R, the maintenance of A1b/137F, and the decline of 3c3.A (Fig.~\ref{fig:nextstrain_forecasts}).
To aid with identification of potential vaccine candidates, we annotated samples in the phylogeny by their estimated distance to the future based on our best model (Fig.~\ref{fig:nextstrain_distance_to_future}).

>>>>

To enable real-time forecasts, we integrated our forecasting framework into our existing open source pathogen surveillance application, Nextstrain \cite{Hadfield2018}, and used our best model to forecast A/H3N2 populations in September 2020.
Prior to finalizing our model coefficients for use in Nextstrain, we tested whether our three best composite models could be improved by learning coefficients per timepoint from the test data.
None of the three models performed better across the test data than the original best model, indicating that the coefficients for our selected best model would be most accurate for live forecasts (Supplemental Fig.~\ref{sup_fig:updated_model_accuracy_and_coefficients_for_natural_populations_across_test_data}).
With the original coefficients, our combined HI cross-immunity, mutational load, and LBI model favored the growth of the currently circulating clade A1b/197R, the maintenance of A1b/137F, and the decline of 3c3.A (Fig.~\ref{fig:nextstrain_forecasts}).
To aid with identification of potential vaccine candidates, we annotated samples in the phylogeny by their estimated distance to the future based on our best model (Fig.~\ref{fig:nextstrain_distance_to_future}).

### 2019-12-20 manuscript/supplement.tex
Add summary of coefficients learned across natural test data
Includes an updated analysis notebook, a new supplemental figure, and a brief
summary in the main results text.

>>>>

\begin{figure*}[ht]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/models-natural-populations-composite-with-updated-coefficients-across-test-data.png}
  \caption{
    Model coefficients and distances to the future for best composite models fit to recent data from natural populations as in Fig.~\ref{fig:unadjusted_model_accuracy_and_coefficients_for_simulated_populations_controls}.
    A) Coefficients and B) distances are shown per test timepoint (N=8).
    In contrast to the results for these models based on fixed coefficients from training/validation, these coefficients were learned for each six-year window prior to the corresponding test timepoint.
    The corresponding distances reflect the model's performance with updated coefficients on what is effectively new validation data.
    The naive model's distance to the future was 6.82 $\pm$ 1.74 AAs for these timepoints.
  }
  \label{sup_fig:updated_model_accuracy_and_coefficients_for_natural_populations_across_test_data}
  \end{center}
\end{figure*}
